### 2018-11-07 Sections/essay_the_global_virtual_quantum_computer.tex
Indexing up to N

The leverage asymmetry will be a key consideration in answering this question, since although both parties benefit on an absolute basis from unification, on a relative basis the weaker party achieves the higher computational leverage. For this reason, it is plausible the global virtual quantum computer will fracture\index{Fracturing}, dissolving into independent smaller virtual quantum computers, divided across geo-strategic or competitive boundaries, with the stronger parties seceding from the union -- even though they would individually benefit computationally from unification, they may not wish the weaker ones to piggyback off them, achieving greater leverage than themselves\footnote{Insert jokes about Greece\index{Greece} and Germany\index{Germany} here --- \textit{Im Wandel der Zeiten -- Eine Geschichte der Zivilisation.}}.

>>>>

The leverage asymmetry will be a key consideration in answering this question, since although both parties benefit on an absolute basis from unification, on a relative basis the weaker party achieves the higher computational leverage. For this reason, it is plausible the global virtual quantum computer will fracture\index{Fracturing}, dissolving into independent smaller virtual quantum computers, divided across geostrategic or competitive boundaries, with the stronger parties seceding from the union -- even though they would individually benefit computationally from unification, they may not wish the weaker ones to piggyback off them, achieving greater leverage than themselves\footnote{Insert jokes about Greece\index{Greece} and Germany\index{Germany} here --- \textit{Im Wandel der Zeiten -- Eine Geschichte der Zivilisation.}}.

### 2018-11-07 Sections/essay_the_quantum_space_race.tex
Resized figs for 1 column
Indexing up to N

The first-generation satellite\index{First-generation quantum satellites} that was recently developed merely contained an entanglement source, and two satellite-to-ground optical links via telescopes armed with laser tracking (Fig.~\ref{fig:first_gen_sat})\index{Laser tracking}. However, this prototype is strictly restricted to distributing entanglement between two ground stations, both simultaneously in line-of-sight of the satellite.

\begin{figure}[!htbp]
\includegraphics[width=0.4\textwidth]{first_gen_satellite}
\captionspacefig \caption{First-generation satellite\index{First-generation quantum satellites} for entanglement distribution. The on-board entanglement source couples to two telescopes, which lock onto independent ground stations using laser tracking\index{Laser tracking}.}\label{fig:first_gen_sat}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{satellite_honeycomb_lattice}
\captionspacefig \caption{A honeycomb lattice\index{Honeycomb lattice} is the lowest order two-dimensional lattice that could be employed to construct a satellite constellation\index{Constellation network} network covering the Earth. Edges represent quantum communications channels, and their intersections are where the satellites reside. Such a network will require next-generation satellites\index{Next-generation quantum satellites} with satellite-to-satellite links.}\label{fig:sat_honeycomb}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{next_gen_satellite}
\captionspacefig \caption{A basic layout for how next-generation quantum satellites might be constructed. Each satellite is capable of both entangled state preparation, as well as entangling measurements. There are three space links for communicating with neighbouring satellites so as to enable a honeycomb lattice configuration, as well as two ground links, as per the first-generation satellite. The switch at the centre must be universal to enable arbitrary pairs of telescopes to couple with either the entanglement source or entangling measurement. The quantum memories\index{Quantum memory} prior to the entangling measurement facilitate synchronising distinct photons with different arrival times such that they can interfere.}\label{fig:next_gen_sat}	
\end{figure}

>>>>

The first-generation satellite\index{First-generation!Quantum satellites} that was recently developed merely contained an entanglement source, and two satellite-to-ground optical links via telescopes armed with laser tracking (Fig.~\ref{fig:first_gen_sat})\index{Laser tracking}. However, this prototype is strictly restricted to distributing entanglement between two ground stations, both simultaneously in line-of-sight of the satellite.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{first_gen_satellite}
\captionspacefig \caption{First-generation satellite\index{First-generation!Quantum satellites} for entanglement distribution. The on-board entanglement source couples to two telescopes, which lock onto independent ground stations using laser tracking\index{Laser tracking}.}\label{fig:first_gen_sat}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{satellite_honeycomb_lattice}
\captionspacefig \caption{A honeycomb lattice\index{Honeycomb lattice} is the lowest order two-dimensional lattice that could be employed to construct a satellite constellation\index{Constellation network} network covering the Earth. Edges represent quantum communications channels, and their intersections are where the satellites reside. Such a network will require next-generation satellites\index{Next-generation quantum satellites} with satellite-to-satellite links.}\label{fig:sat_honeycomb}	
\end{figure}

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.65\textwidth]{next_gen_satellite}
\else
\includegraphics[clip=true, width=0.475\textwidth]{next_gen_satellite}
\fi
\captionspacefig \caption{A basic layout for how next-generation quantum satellites might be constructed. Each satellite is capable of both entangled state preparation, as well as entangling measurements. There are three space links for communicating with neighbouring satellites so as to enable a honeycomb lattice configuration, as well as two ground links, as per the first-generation satellite. The switch at the centre must be universal to enable arbitrary pairs of telescopes to couple with either the entanglement source or entangling measurement. The quantum memories\index{Quantum memory} prior to the entangling measurement facilitate synchronising distinct photons with different arrival times such that they can interfere.}\label{fig:next_gen_sat}	
\end{figure}

### 2018-11-07 Sections/essay_to_the_future_QKD.tex
Indexing up to N

\dropcap{Q}{uantum} key distribution (QKD) is the first quantum information task to reach commercialisation. Its purpose is to distribute a secret-key between two trusted parties who share a quantum channel, as well as a classical channel for authentication. Unlike current cryptography systems, which are secure based on the presumed limitations of an adversary's computer (\textit{computational security}\index{Computational security}), the security of QKD is based on the laws of quantum mechanics, providing guaranteed security unless our understanding of quantum physics is inherently wrong (\textit{information theoretic security}\index{Information theoretic security}).

@@

The quantum channel is subject to possible manipulation by Eve. The task of Alice and Bob is thus to guarantee security against an adversarial eavesdropper. The typical protocol assumes that Alice and Bob do not share any secret to begin with. The origin of the security of QKD springs from the fundamentals of quantum mechanics, that is, any act of measurement by an observer on a quantum state necessarily induces a change in the state -- measurement collapse\index{Measurement collapse}. This means that in combination with classical communication, actions of an eavesdropper cannot go undetected, ruling out intercept-resend attacks\index{Intercept-resend attacks} by Eve.

@@

For continuous-variable\index{Continuous-variables} QKD systems, increasing the bandwidth of the homodyne/heterodyne detectors\index{Homodyne detectors}\index{Heterodyne detectors} whilst keeping the electronic noise low is essential.

@@

However, currently, neither of the protocols out-compete the more mature decoy-state BB84\index{BB84}\index{Decoy-states}.

@@

This provides strong evidence that secure quantum communication with imperfect sources is feasible \cite{bib:diamanti2016practical}. Intuitively, QKD with imperfect sources is viable because by assuming that states prepared by Alice are qubits, Eve cannot unambiguously discriminate Alice's states \cite{bib:diamanti2016practical} -- quantum measurement collapses quantum states\index{Measurement collapse}.

@@

The MDI-QKD protocol has been extended to the continuous variable\index{Continuous-variables} framework. However, this system requires homodyne detectors\index{Homodyne detectors} with efficiency $>85\%$, and a reliable phase reference\index{Phase reference} between Alice and Bob.

We have discussed some significant remaining challenges in QKD. These range from theoretical security proofs to hardware developments. Advances in QKD will not only enable point-to-point quantum communication\index{Point-to-point communication}, but have implications for a range of network applications, such as quantum secret sharing\index{Quantum secret sharing} \cite{bib:cleve1999share, bib:PhysRevA.61.042311, bib:PhysRevA.71.044301}, blind quantum computing\index{Blind quantum computing} \cite{bib:broadbent2009universal, bib:barz2012demonstration}, quantum anonymous broadcasting\index{Quantum anonymous broadcasting} \cite{bib:christandl2005quantum}, and many more.

>>>>

\dropcap{Q}{uantum} key distribution (QKD) is the first quantum information task to reach commercialisation. Its purpose is to distribute a secret-key between two trusted parties who share a quantum channel, as well as a classical channel for authentication. Unlike current cryptography systems, which are secure based on the presumed limitations of an adversary's computer (\textit{computational security}\index{Computational security}), the security of QKD is based on the laws of quantum mechanics, providing guaranteed security unless our understanding of quantum physics is inherently wrong (\textit{information theoretic security}\index{Information-theoretic security}).

@@

The quantum channel is subject to possible manipulation by Eve. The task of Alice and Bob is thus to guarantee security against an adversarial eavesdropper. The typical protocol assumes that Alice and Bob do not share any secret to begin with. The origin of the security of QKD springs from the fundamentals of quantum mechanics, that is, any act of measurement by an observer on a quantum state necessarily induces a change in the state -- measurement collapse\index{Measurement!Collapse}. This means that in combination with classical communication, actions of an eavesdropper cannot go undetected, ruling out intercept-resend attacks\index{Intercept-resend attacks} by Eve.

@@

For continuous-variable\index{Continuous-variables} QKD systems, increasing the bandwidth of the homodyne/heterodyne detectors\index{Homodyne detection}\index{Heterodyne detectors} whilst keeping the electronic noise low is essential.

@@

However, currently, neither of the protocols out-compete the more mature decoy-state BB84\index{BB84 protocolion
}\index{Decoy states}.

@@

This provides strong evidence that secure quantum communication with imperfect sources is feasible \cite{bib:diamanti2016practical}. Intuitively, QKD with imperfect sources is viable because by assuming that states prepared by Alice are qubits, Eve cannot unambiguously discriminate Alice's states \cite{bib:diamanti2016practical} -- quantum measurement collapses quantum states\index{Measurement!Collapse}.

@@

The MDI-QKD protocol has been extended to the continuous variable\index{Continuous-variables} framework. However, this system requires homodyne detectors\index{Homodyne detection} with efficiency $>85\%$, and a reliable phase reference\index{Phase reference} between Alice and Bob.

We have discussed some significant remaining challenges in QKD. These range from theoretical security proofs to hardware developments. Advances in QKD will not only enable point-to-point quantum communication\index{Point-to-point communication}, but have implications for a range of network applications, such as quantum secret sharing\index{Quantum secret sharing} \cite{bib:cleve1999share, bib:PhysRevA.61.042311, bib:PhysRevA.71.044301}, blind quantum computing\index{Blind quantum computation} \cite{bib:broadbent2009universal, bib:barz2012demonstration}, quantum anonymous broadcasting\index{Quantum anonymous broadcasting} \cite{bib:christandl2005quantum}, and many more.

### 2018-11-07 Sections/introduction.tex
Indexing up to N

From a computational complexity\index{Computational complexity theory} theorist's perspective, it is strongly believed that the complexity classes of problems efficiently solvable on classical computers (\textbf{P} \& \textbf{BPP}\index{P}\index{BPP}) and quantum computers (\textbf{BQP}\index{BQP}) are distinct. Specifically, it is believed that \mbox{$\mathbf{BPP}\subset\mathbf{BQP}$}. If this conjecture is correct, it implies the existence of quantum algorithms super-polynomially faster than the best classical ones, and that the ECT thesis is not correct. More specifically, Fig.~\ref{fig:complexity_classes} illustrates the believed relationships between some of the most important complexity classes relevant to quantum computing.

@@

Our treatment of quantum networks will be optics-heavy, based on the reasonable assumption that communications channels will almost certainly be optical, albeit with many possible choices of optical states and mediums. However, this does not preclude non-optical systems from representing quantum information that is not in transit, and we consider such `hybrid' architectures\index{Hybrid architectures} in detail, as well as the interfacing between optical and non-optical systems. Indeed, it is almost certain that future large-scale quantum computers will not be all-optical, necessitating interfacing different physical architectures. We accommodate for this requirement in the design of the QTCP.

>>>>

From a computational complexity\index{Computational complexity} theorist's perspective, it is strongly believed that the complexity classes of problems efficiently solvable on classical computers (\textbf{P} \& \textbf{BPP}\index{P}\index{BPP}) and quantum computers (\textbf{BQP}\index{BQP}) are distinct. Specifically, it is believed that \mbox{$\mathbf{BPP}\subset\mathbf{BQP}$}. If this conjecture is correct, it implies the existence of quantum algorithms super-polynomially faster than the best classical ones, and that the ECT thesis is not correct. More specifically, Fig.~\ref{fig:complexity_classes} illustrates the believed relationships between some of the most important complexity classes relevant to quantum computing.

@@

Our treatment of quantum networks will be optics-heavy, based on the reasonable assumption that communications channels will almost certainly be optical, albeit with many possible choices of optical states and mediums. However, this does not preclude non-optical systems from representing quantum information that is not in transit, and we consider such `hybrid' architectures\index{Hybrid!Architectures} in detail, as well as the interfacing between optical and non-optical systems. Indeed, it is almost certain that future large-scale quantum computers will not be all-optical, necessitating interfacing different physical architectures. We accommodate for this requirement in the design of the QTCP.

### 2018-11-07 Sections/models_for_quantum_computation.tex
Indexing up to N

Fig.~\ref{fig:eg_circuit} illustrates a simple 3-qubit quantum circuit comprising all of these elements. The interpretation of this diagram is as follows:
\begin{itemize}
	\item Horizontal lines represent individual qubits.
	\item Time flows from left to right (feedback is not allowed in the typical formalism for this representation).
	\item The three input qubits are labelled on the far-left as $\ket{\psi_1}$, $\ket{\psi_2}$ and $\ket{\psi_3}$.
	\item Single-qubit gates are denoted as boxes containing the name of the associated unitary operation. Here, the examples are the Hadamard ($\hat{H}$), Pauli bit-flip ($\hat{X}$), Pauli bit-phase-flip ($\hat{Y}$), and Pauli phase-flip ($\hat{Z}$) gates\index{Pauli operators}\index{Hadamard gate},
	\begin{align}
		\hat{H} &= \frac{1}{\sqrt{2}}\begin{pmatrix}
		1 & 1 \\
		1 & -1
		\end{pmatrix},\nonumber \\
		\hat{X} &= \begin{pmatrix}
		0 & 1 \\
		1 & 0
		\end{pmatrix},\nonumber \\
		\hat{Y} &= \begin{pmatrix}
		0 & -i \\
		i & 0
		\end{pmatrix},\nonumber \\
		\hat{Z} &= \begin{pmatrix}
		1 & 0 \\
		0 & -1
		\end{pmatrix}.
	\end{align}
	\item 2-qubit gates are denoted by vertical lines between the respective qubits.
	\item The maximally-entangling 2-qubit controlled-NOT (CNOT) gate\index{Controlled-NOT (CNOT) gate} is denoted via a control ($\bullet$) and a target ($\oplus$),
	\begin{align}
		\hat{\mathrm{CNOT}}=\begin{pmatrix}
		1 & 0 & 0 & 0 \\
		0 & 1 & 0 & 0 \\
		0 & 0 & 0 & 1 \\
		0 & 0 & 1 & 0
		\end{pmatrix}.
	\end{align}
	This is the quantum equivalent of the classical XOR gate, flipping the target ($\hat{X}$) if the control is on.
	\item All quantum gates have the same number of input as output qubits. This is a necessary condition for the unitarity of quantum gates (\mbox{$\hat{U}^\dag \hat{U} = \hat{\mathbb{I}}$}).
	\item The maximally-entangling 2-qubit controlled-phase (CZ)\index{Controlled-Z (CZ) gate} gate is denoted by two targets ($\bullet$) (the gate operates symmetrically on its two qubits),
	\begin{align}
		\hat{\mathrm{CZ}}=\begin{pmatrix}
		1 & 0 & 0 & 0 \\
		0 & 1 & 0 & 0 \\
		0 & 0 & 1 & 0 \\
		0 & 0 & 0 & -1
		\end{pmatrix},
	\end{align}
	applying a phase-gate ($\hat{Z}$) to the target if the control is on.
	\item The `meter' symbol represents a classical measurement in the Pauli $\hat{Z}$-basis (the computational or logical basis).
	\item Double lines represent classical feedforward of measurement outcomes, controlling a subsequent gate.
\end{itemize}

@@

\subsection{Cluster states} \label{sec:CSQC} \index{Cluster state model}

@@

In the graph, vertices represent qubits initialised into the,
\begin{align}
	\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1}),
\end{align}
state, and edges represent the application of maximally entangling CZ gates between vertices,
\begin{align}
	\ket\psi_\mathrm{cluster} = \prod_{e\in E} \hat{\mathrm{CZ}}_e \cdot \bigotimes_{v\in V}\ket{+}_v.
\end{align}
Alternately, but equivalently, cluster states may be defined in the stabiliser formalism\index{Stabiliser formalism}. Specifically, a cluster state is defined to be the joint +1 eigenstate of all the stabilisers,
\begin{align} \label{eq:CS_stab} \index{Cluster state stabilisers}
	\hat{S}_v = \hat{X}_v \prod_{i\in n_v} \hat{Z}_i,
\end{align}
where there is one stabiliser $\hat{S}_v$ per vertex $v$, and $n_v$ is the set of vertices neighbouring $v$. The cluster state therefore satisfies,
\begin{align}
	\hat{S}_v\ket\psi_\mathrm{cluster} = \ket\psi_\mathrm{cluster}\,\forall\, v,
\end{align}
and the full set of stabilisers, $\hat{S}_v$, over all vertices $v$ is sufficient to fully characterise the cluster state, $\ket{\psi}_\mathrm{cluster}$, for a given graph topology.

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{cluster_identities} \index{Cluster state identities}
	\captionspacefig \caption{Several cluster state identities, demonstrated in the case of linear clusters. (a) a CZ gate between two qubits creates an edge between them in the graph. (b) Measurement of a qubit in the Pauli $\hat{Y}$ basis removes that qubit from the graph, whilst creating new edges between the neighbouring qubits. (c) Measurement of a qubit in the Pauli $\hat{Z}$ basis removes that qubit and any neighbouring edges. (d) Measurement of a qubit in the Pauli $\hat{X}$ basis removes that qubit, leaving one of its neighbours as a `dangling node'.} \label{fig:cluster_ident} 
\end{figure}

@@

The first is to use the ideas of \textit{micro-clusters}\index{Micro-cluster states} and cluster state recycling\index{Cluster state recycling} to incrementally build up larger clusters, progressing as a random walk\index{Random walks}, which is biased in the direction of state growth. This approach is discussed in more detail in Secs.~\ref{sec:CS_LO} \& \ref{sec:module}.

@@

As with conventional QEC, this introduces (potentially large, but efficient) overheads associated with encoding logical qubits into fault-tolerant codes. Similarly, there is the notion of \textit{fault-tolerance thresholds}\index{Fault-tolerance thresholds} -- thresholds on gate error rates that must be achieved if fault-tolerant execution is to be successful. These thresholds are typically depressingly low (well below 1\%) and are the primary reason humanity has not yet achieved scalable quantum computing.

>>>>

Fig.~\ref{fig:eg_circuit} illustrates a simple 3-qubit quantum circuit comprising all of these elements. The interpretation of this diagram is as follows:
\begin{itemize}
	\item Horizontal lines represent individual qubits.
	\item Time flows from left to right (feedback is not allowed in the typical formalism for this representation).
	\item The three input qubits are labelled on the far-left as $\ket{\psi_1}$, $\ket{\psi_2}$ and $\ket{\psi_3}$.
	\item Single-qubit gates are denoted as boxes containing the name of the associated unitary operation. Here, the examples are the Hadamard ($\hat{H}$), Pauli bit-flip ($\hat{X}$), Pauli bit-phase-flip ($\hat{Y}$), and Pauli phase-flip ($\hat{Z}$) gates\index{Pauli operators}\index{Hadamard!Gate},
	\begin{align}
		\hat{H} &= \frac{1}{\sqrt{2}}\begin{pmatrix}
		1 & 1 \\
		1 & -1
		\end{pmatrix},\nonumber \\
		\hat{X} &= \begin{pmatrix}
		0 & 1 \\
		1 & 0
		\end{pmatrix},\nonumber \\
		\hat{Y} &= \begin{pmatrix}
		0 & -i \\
		i & 0
		\end{pmatrix},\nonumber \\
		\hat{Z} &= \begin{pmatrix}
		1 & 0 \\
		0 & -1
		\end{pmatrix}.
	\end{align}
	\item 2-qubit gates are denoted by vertical lines between the respective qubits.
	\item The maximally-entangling 2-qubit controlled-NOT (CNOT) gate\index{Controlled-NOT (CNOT) gates} is denoted via a control ($\bullet$) and a target ($\oplus$),
	\begin{align}
		\hat{\mathrm{CNOT}}=\begin{pmatrix}
		1 & 0 & 0 & 0 \\
		0 & 1 & 0 & 0 \\
		0 & 0 & 0 & 1 \\
		0 & 0 & 1 & 0
		\end{pmatrix}.
	\end{align}
	This is the quantum equivalent of the classical XOR gate, flipping the target ($\hat{X}$) if the control is on.
	\item All quantum gates have the same number of input as output qubits. This is a necessary condition for the unitarity of quantum gates (\mbox{$\hat{U}^\dag \hat{U} = \hat{\mathbb{I}}$}).
	\item The maximally-entangling 2-qubit controlled-phase (CZ)\index{Controlled-Z (CZ) gates} gate is denoted by two targets ($\bullet$) (the gate operates symmetrically on its two qubits),
	\begin{align}
		\hat{\mathrm{CZ}}=\begin{pmatrix}
		1 & 0 & 0 & 0 \\
		0 & 1 & 0 & 0 \\
		0 & 0 & 1 & 0 \\
		0 & 0 & 0 & -1
		\end{pmatrix},
	\end{align}
	applying a phase-gate ($\hat{Z}$) to the target if the control is on.
	\item The `meter' symbol represents a classical measurement in the Pauli $\hat{Z}$-basis (the computational or logical basis).
	\item Double lines represent classical feedforward of measurement outcomes, controlling a subsequent gate.
\end{itemize}

@@

\subsection{Cluster states} \label{sec:CSQC} \index{Cluster states!Model for quantum computation}

@@

In the graph, vertices represent qubits initialised into the,
\begin{align}
	\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1}),
\end{align}
state, and edges represent the application of maximally entangling CZ gates between vertices,
\begin{align}
	\ket\psi_\mathrm{cluster} = \prod_{e\in E} \hat{\mathrm{CZ}}_e \cdot \bigotimes_{v\in V}\ket{+}_v.
\end{align}
Alternately, but equivalently, cluster states may be defined in the stabiliser formalism\index{Stabiliser formalism}. Specifically, a cluster state is defined to be the joint +1 eigenstate of all the stabilisers,
\begin{align} \label{eq:CS_stab} \index{Cluster states!Stabilisers}
	\hat{S}_v = \hat{X}_v \prod_{i\in n_v} \hat{Z}_i,
\end{align}
where there is one stabiliser $\hat{S}_v$ per vertex $v$, and $n_v$ is the set of vertices neighbouring $v$. The cluster state therefore satisfies,
\begin{align}
	\hat{S}_v\ket\psi_\mathrm{cluster} = \ket\psi_\mathrm{cluster}\,\forall\, v,
\end{align}
and the full set of stabilisers, $\hat{S}_v$, over all vertices $v$ is sufficient to fully characterise the cluster state, $\ket{\psi}_\mathrm{cluster}$, for a given graph topology.

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{cluster_identities} \index{Cluster states!Identities}
	\captionspacefig \caption{Several cluster state identities, demonstrated in the case of linear clusters. (a) a CZ gate between two qubits creates an edge between them in the graph. (b) Measurement of a qubit in the Pauli $\hat{Y}$ basis removes that qubit from the graph, whilst creating new edges between the neighbouring qubits. (c) Measurement of a qubit in the Pauli $\hat{Z}$ basis removes that qubit and any neighbouring edges. (d) Measurement of a qubit in the Pauli $\hat{X}$ basis removes that qubit, leaving one of its neighbours as a `dangling node'.} \label{fig:cluster_ident} 
\end{figure}

@@

The first is to use the ideas of \textit{micro-clusters}\index{Micro-cluster states} and cluster state recycling\index{Cluster states!Recycling} to incrementally build up larger clusters, progressing as a random walk\index{Random walks}, which is biased in the direction of state growth. This approach is discussed in more detail in Secs.~\ref{sec:CS_LO} \& \ref{sec:module}.

@@

As with conventional QEC, this introduces (potentially large, but efficient) overheads associated with encoding logical qubits into fault-tolerant codes. Similarly, there is the notion of \textit{fault-tolerance thresholds}\index{Fault-tolerance!Thresholds} -- thresholds on gate error rates that must be achieved if fault-tolerant execution is to be successful. These thresholds are typically depressingly low (well below 1\%) and are the primary reason humanity has not yet achieved scalable quantum computing.

### 2018-11-07 Sections/network_algorithms.tex
Indexing up to N

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum-cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum-cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\subsection{Minimum spanning tree} \label{sec:min_tree} \index{Minimum spanning tree algorithm}

>>>>

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\log |V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum-cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\log |V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\log |V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree!Algorithm}\index{Minimum-cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

\subsection{Minimum spanning tree} \label{sec:min_tree} \index{Minimum spanning tree!Algorithm}

### 2018-11-07 Sections/network_topologies.tex
Indexing up to N

\subsection{Hybrid} \index{Hybrid topologies}

@@

A feature of scale-free networks of especial interest in the context of computer networks is their robustness against node failure. Suppose we constructed a percolated (Sec.~\ref{sec:perc_topol}) instance of a typical scale-free network. Such a network is highly robust against \textit{random} node/edge deletions compared to many other graph constructions, in the sense that a relatively large number of failures must occur to disconnect the graph. This makes the scale-free network characteristic a particularly attractive one from the perspective of the failure-tolerance of a network. It should be noted that, on the other hand, a scale-free network is highly vulnerable to \textit{targeted} node/edge deletions, that specifically target the highly-connected nodes. A targeted attack against major hubs could disconnect the network with relatively few successful attacks. This brings with it important geo-strategic\index{Geo-strategic politics} considerations when constructing network infrastructure.

@@

A key feature of any network topology is its robustness against node or channel failures. This is important from the perspective of naturally occurring hardware faults, and also from a geo-strategic perspective, where adversaries may be launching attacks against the network. In general, there are two main contributing factors to network robustness:
\begin{itemize}
	\item Redundancy\index{Redundancy}: the number of redundant paths between two points in a graph stipulates how many backups there are to finding a route to a destination in the advent of one route failing.
	\item Diameter\index{Diameter}: the chance of a data packet encountering a faulty node/channel increases with the number of hops required to the reach its destination. Graphs with smaller diameter are hence less vulnerable.
\end{itemize}

>>>>

\subsection{Hybrid} \index{Hybrid!Topologies}

@@

A feature of scale-free networks of especial interest in the context of computer networks is their robustness against node failure. Suppose we constructed a percolated (Sec.~\ref{sec:perc_topol}) instance of a typical scale-free network. Such a network is highly robust against \textit{random} node/edge deletions compared to many other graph constructions, in the sense that a relatively large number of failures must occur to disconnect the graph. This makes the scale-free network characteristic a particularly attractive one from the perspective of the failure-tolerance of a network. It should be noted that, on the other hand, a scale-free network is highly vulnerable to \textit{targeted} node/edge deletions, that specifically target the highly-connected nodes. A targeted attack against major hubs could disconnect the network with relatively few successful attacks. This brings with it important geostrategic\index{Geostrategic politics} considerations when constructing network infrastructure.

@@

A key feature of any network topology is its robustness against node or channel failures. This is important from the perspective of naturally occurring hardware faults, and also from a geostrategic perspective, where adversaries may be launching attacks against the network. In general, there are two main contributing factors to network robustness:
\begin{itemize}
	\item Redundancy\index{Redundancy}: the number of redundant paths between two points in a graph stipulates how many backups there are to finding a route to a destination in the advent of one route failing.
	\item Diameter\index{Diameter}: the chance of a data packet encountering a faulty node/channel increases with the number of hops required to the reach its destination. Graphs with smaller diameter are hence less vulnerable.
\end{itemize}
